---
title: "Supriya Sule: A Parliamentary Record"
subtitle: "Analysis of Starred Questions · 16th, 17th & 18th Lok Sabha"
author: "Piyush Zaware"
date: "June 2026"
format:
  html:
    theme:
      light: [flatly, custom.scss]
    toc: true
    toc-location: right
    toc-title: "Contents"
    toc-depth: 2
    smooth-scroll: true
    code-fold: true
    fig-align: center
    fig-cap-location: bottom
    self-contained: true
    html-math-method: katex
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
source("code/E1_sule_report.R")
```

::: {.hero}
# Supriya Sule

::: {.subtitle}
MP, Baramati (Maharashtra) · NCP-SP · 16th, 17th and 18th Lok Sabha
:::

::: {.meta}
Piyush Zaware · University of Chicago
:::

::: {.badge-row}
::: {.badge-item}
78 Starred Questions
:::
::: {.badge-item}
3 Lok Sabhas
:::
::: {.badge-item}
Baramati, Maharashtra
:::
::: {.badge-item}
NCP-SP
:::
:::
:::

```{r stats}
n_q      <- nrow(sule)
n_min    <- n_distinct(sule$ministry_clean)
n_cosign <- nrow(cosign_count)
top_min  <- min_compare$ministry_clean[1]
top_n_min <- min_compare$sule_n[1]
```

::: {.stat-row}
::: {.stat}
::: {.stat-num}
`r n_q`
:::
::: {.stat-label}
Starred Questions
:::
:::

::: {.stat}
::: {.stat-num}
`r sum(sule$is_primary)`
:::
::: {.stat-label}
As Primary Questioner
:::
:::

::: {.stat}
::: {.stat-num}
`r n_min`
:::
::: {.stat-label}
Ministries Targeted
:::
:::

::: {.stat}
::: {.stat-num}
`r n_cosign`
:::
::: {.stat-label}
Distinct Co-Signatories
:::
:::
:::

---

::: {.callout-note}
## TL;DR: Five things to know

1. **Agriculture dominates.** She questions the Agriculture Ministry at 3× the parliament-wide rate. Baramati is sugarcane country.
2. **Sustained pressure.** Agriculture appears across the most sessions of any ministry. This is not a one-off.
3. **Coordinated bloc.** She co-signs as frequently as she leads: 39 questions each way.
4. **Calmer than her own party.** 0% adversarial tone vs ~17% for INC/NCP peers. She asks for data, not drama.
5. **Declined over time.** 47 questions in the 16th LS, 21 in the 17th, 10 in the 18th (ongoing).
:::

---

## Ministry Focus

**She goes after Agriculture above everything else:** `r top_n_min` questions, more than Railways and Finance combined. Baramati's sugar cooperatives, irrigation access, and MSP policy explain why.

::: {.callout-note}
## Key takeaway
Agriculture gets **3× her expected share.** Every other ministry is roughly in line with parliament norms.
:::

```{r fig-ministry, fig.cap="Orange = Supriya Sule's share. Grey = parliament-wide average. Agriculture is the clear outlier."}
p_ministry
```

### Over- vs under-questioning

Pearson residuals show which ministries she hits harder or softer than expected given her overall activity level.

```{r fig-excess, fig.cap="Positive (orange) = she questions this ministry more than her size predicts. Negative (blue) = she leaves it alone."}
p_excess
```

---

## Activity Over Time

Her output dropped across terms: **47 → 21 → 10** questions across the 16th, 17th and 18th Lok Sabha. The 18th is still in early sessions, which partly explains the drop.

::: {.callout-note}
## Key takeaway
She is an equal primary/co-signatory split (39/39). Maharashtra NCP coordinates questions as a bloc, not individually.
:::

```{r fig-temporal, fig.cap="Orange = she is the primary questioner. Grey = she is co-signing. The split is almost exactly 50/50."}
p_temporal
```

---

## Topic Evolution

Did her agenda shift across terms? TF-IDF run separately within each Lok Sabha reveals which words are distinctive to each period.

::: {.callout-note}
## Key takeaway
Look for words that appear only in the 17th or 18th but not the 16th. New terms signal new priorities; returning terms signal sustained campaigns.
:::

```{r fig-topic-evolution, fig.cap="Top words that most distinguish each Lok Sabha period from the others. A word appearing only in one term entered or left her agenda mid-career."}
p_topic_evolution
```

### Ministry share over time

Which ministries grew, which shrank?

```{r fig-ministry-trend, fig.cap="Share of her starred questions per ministry, by Lok Sabha. Rising lines = growing focus; falling lines = deprioritised."}
p_ministry_trend
```

---

## Ministry Persistence

Which ministries did she return to across multiple sessions? Repeat questioning signals a sustained accountability campaign, not a one-off.

::: {.callout-note}
## Key takeaway
```{r persist-callout}
top_persist <- persist_summary %>% slice_max(n_sessions, n = 1)
cat(paste0(
  "**", top_persist$ministry_clean, "** is her most persistent target: ",
  top_persist$n_sessions, " distinct sessions, ",
  top_persist$total_q, " total questions."
))
```
:::

```{r fig-persistence, fig.cap="Each cell = questions to that ministry in that session. Dashed lines divide Lok Sabhas. Colour across many columns = sustained pressure campaign."}
p_persistence
```

```{r persist-table}
persist_summary %>%
  select(ministry_clean, n_sessions, total_q) %>%
  rename(Ministry = ministry_clean,
         `Sessions appeared` = n_sessions,
         `Total questions` = total_q) %>%
  knitr::kable()
```

---

## Topics

```{r fig-topics, eval=file.exists(file.path(TABDIR, "sule_topics.csv")), fig.cap="BERTopic clusters assigned to her starred questions. Fill = how much more she concentrates on this topic vs the rest of parliament."}
if (exists("p_topics")) p_topics
```

### Her fingerprint words

Words she uses far more than any other MP, compared using TF-IDF against the full parliament corpus.

::: {.callout-note}
## Key takeaway
Her word cloud is: **sugarcane, cooperative, irrigation, Pune, Baramati, women.** Constituency-driven, not rhetorical.
:::

```{r fig-tfidf, fig.cap="Higher bar = more distinctive to her questions. Common parliamentary boilerplate words are stripped out."}
p_tfidf
```

---

## Tone

Does she ask questions aggressively or neutrally? VADER sentiment scores each question's language.

::: {.callout-note}
## Key takeaway
**0% adversarial rate.** None of her questions score below −0.05 on VADER. Her INC/NCP party peers: ~17%. She asks for facts, not fights.
:::

```{r sent-stats}
if (exists("sule_sent")) {
  adv_rate  <- round(100 * mean(sule_sent$sent_compound <= -0.05, na.rm = TRUE), 1)
  avg_score <- round(mean(sule_sent$sent_compound, na.rm = TRUE), 3)
  peer_avg  <- round(mean(peer_sent$sent_compound, na.rm = TRUE), 3)
  peer_adv  <- round(100 * mean(peer_sent$sent_compound <= -0.05, na.rm = TRUE), 1)
}
```

Her mean compound score: **`r avg_score`**. Peer average: `r peer_avg`. She is more neutral than her own party bloc, which is unusual for an opposition MP across three terms.

```{r fig-sentiment, fig.cap="Distribution of VADER compound scores. Further right = more neutral or positive framing. Supriya Sule (orange) skews right of her INC/NCP peers (navy)."}
if (exists("p_sent")) p_sent
```

---

## Co-Signatories

```{r cosign-analysis}
top_cosign <- cosign_count %>%
  filter(!is.na(party_family)) %>%
  slice_max(n_questions, n = 3)
```

::: {.callout-note}
## Key takeaway
Top three co-signatories: **`r str_to_title(top_cosign$cosignatory[1])`** (`r top_cosign$n_questions[1]` questions), **`r str_to_title(top_cosign$cosignatory[2])`** (`r top_cosign$n_questions[2]`), **`r str_to_title(top_cosign$cosignatory[3])`** (`r top_cosign$n_questions[3]`).
:::

```{r fig-cosign, fig.cap="MPs who co-signed the most questions with her. Party label and constituency shown per bar."}
p_cosign
```

---

## Sample Questions

```{r sample-qs}
sample_qs <- sule %>%
  mutate(text_c = map_chr(question_text, function(t) {
    if (is.na(t)) return("")
    t <- str_replace_all(t, "##.*?\\n", " ")
    t <- str_replace_all(t, "\\([a-z]\\)", " ")
    t <- str_squish(t)
    str_trunc(t, 400)
  })) %>%
  filter(nchar(text_c) > 80) %>%
  group_by(ministry_clean) %>%
  slice_head(n = 1) %>%
  ungroup() %>%
  arrange(desc(is_primary)) %>%
  slice_head(n = 5) %>%
  select(lok_no, session_no, ministry_clean, text_c)
```

```{r sample-table}
sample_qs %>%
  mutate(
    Session  = paste0(lok_no, "th LS · S", session_no),
    Ministry = ministry_clean,
    Question = text_c
  ) %>%
  select(Session, Ministry, Question) %>%
  knitr::kable(col.names = c("Lok Sabha", "Ministry", "Question"))
```

---

::: {style="font-size: 0.8rem; color: #888; margin-top: 3rem; border-top: 1px solid #E8DDD0; padding-top: 1rem;"}
Prepared by Piyush Zaware · University of Chicago · Unsupervised ML Project
Data: opensansad/lok-sabha-qa (HuggingFace) · 16th–18th Lok Sabha starred questions
Analysis: BERTopic, VADER sentiment, TF-IDF (tidytext)
Research document. Not for public distribution.
:::
